---
title: "p8105_hw1_sw3866"
author: "Siyan Wen"
date: "2023-09-19"
output: html_document
---
## Problem 1
```{r}
#Load the library
library(moderndive)
library(tidyverse)
#Load the dataset
data("early_january_weather")
#Accessing data
help("early_january_weather")
```
This dataset contains hourly meterological data for LGA,JFK and EWR in early January 2013. In total, it has 15 variables including origin, year, month, day, hour, temp, dewp,humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib and time_hour. The size of this dataset is `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.The mean temperature of this dataset is `r mean (early_january_weather $ temp)` °F.
```{r}
## Scatterplot of Temperature and Humidity over time in hours.
ggplot(early_january_weather,aes(x=time_hour,y=temp,color = humid))+geom_point()
```
The temperature gradually increased in the range of approximately 25 to 55 degrees Fahrenheit from January 1st to mid-January. Additionally, the humidity fluctuated from January 1st to January 12th and has significant increase from January 12th to the 14th for around two days.
```{r}
##Export the scatterplot
ggsave("scatterplot.pdf")
```

## Problem 2
```{r}
#Create a data frame
df<-tibble(random_sample=rnorm(n = 10, mean = 0, sd = 1),
logical=random_sample>0,
charactor=c("a","b","c","a","b","c","a","b","c","a"),
factor=factor(x=charactor,labels=c("large","small","medium")))
```
```{r}
# Use pull function
col_1=pull(df,var=random_sample)
col_2=pull(df,var=logical)
col_3=pull(df,var=charactor)
col_4=pull(df,var=factor)
```
```{r}
# Take the mean of each variable in the dataset
mean(col_1)
mean(col_2)
mean(col_3)
mean(col_4)
```
The "mean" function worked for numeric or logical variables. Column 1 is numeric variable and column 2 is logical variable. So, the "mean" function worked for column 1 and column 2. However, the "mean function did not worked for character and factor variables. So, it did not works for column 3 or column 4 because they are either character or factor variable.


```{r,eval=FALSE}
#the mean of each variable in dataset using as.numeric
mean(as.numeric(col_1))
mean(as.numeric(col_2))
mean(as.numeric(col_3))
mean(as.numeric(col_4))
```
After using the "as.numeric" function, the "mean" function worked for column 1,2 and 4,but it still did not worked for column 3. The "as.numeric"function is used to convert a character/factor vector into a numeric vector. However,it cannot convert a character vector into a numeric vector when all the elements inside that character vector are letters. It can only convert factor vector that have been treated as three different levels into numeric vector. Three different levels have been convert into numerical values as 1, 2 and 3 under the "as.numeric"function. Therefore, the "mean" function worked for column 4 this time.  


