---
title: "p8105_hw1_sw3866"
author: "Siyan Wen"
date: "2023-09-19"
output: html_document
---
## Problem 1
```{r}
#Load the library
library(moderndive)
library(tidyverse)
#Load the dataset
data("early_january_weather")
#Accessing data
help("early_january_weather")
```
This dataset contains hourly meterological data for LGA,JFK and EWR in early January 2013. In total, it has 15 variables including origin, year, month, day, hour, temp, dewp,humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib and time_hour. The size of this dataset is `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.The mean temperature of this dataset is `r mean (early_january_weather $ temp)` °F.
```{r}
## Scatterplot of Temperature and Humidity over time in hours.
ggplot(early_january_weather,aes(x=time_hour,y=temp,color = humid))+geom_point()
ggsave("scatterplot.pdf")
```
The temperature gradually increased in the range of approximately 25 to 55 degrees Fahrenheit from January 1st to mid-January. Additionally, the humidity fluctuated slightly from January 1st to January 12th, and there was a significant increase in humidity from January 12th to the 14th for around two days.

## Problem 2
